Prediction of 90-day mortality after Total Hip Arthroplasty: a simplified and externally validated model based on observational registry data from Sweden, England and Wales

### 2020-05-11 reports/article.Rmd
adjusted CI to LR format. Fix #10.

get_auc <- function(mod) {
  subset(
    brlasso_tbl_auc, 
    Model == mod & 
      `Age as` %in% c(NA, "main effect"), 
    "AUC", 
    drop = TRUE
  ) %>% 
  {sprintf("(AUC = %s", gsub(" (", ", 95 % CI: ",., fixed = TRUE))} %>% 
  ud()
}

>>>>

get_auc <- function(mod) {
  subset(
    brlasso_tbl_auc, 
    Model == mod & 
      `Age as` %in% c(NA, "main effect"), 
    "AUC", 
    drop = TRUE
  ) %>% 
  {sprintf("(AUC = %s", gsub(" (", ", 95 % CI ",., fixed = TRUE))} %>% 
  ud()
}
